Pesticides pollution of small streams in Germany

### 2016-07-26 article.tex
supplement + ms

Small water bodies are important refuges of biodiversity \citep{davies_comparison_2008} and enabling downstream colonisation of 
At the same time they may be exposed to a high risk of pesticide contamination from adjacent agricultural areas and low dilution effects \citep{liess_determination_1999}.

% Although small waterbodies make up most

% running  water  
% with  at  least  10km2  catchment  area

% However, very little is know about the pollution of such streams. 
% The

% Small waterbodies
% underestimation of grab sampling (Stehle et al. 2013).

The aim of this study was to compile monitoring data on a national scale and to answer the questions: \\
(i) Is the currently available monitoring data a representative description of the pollution situation? \\
(ii) Are small agricultural waters more polluted compared to bigger streams? Are there thresholds? \\
(iii)  How polluted are small streams and which pesticides are responsible?

@@

The compiled dataset comprised only a small fraction of standing waters and most of the samples where sampled via grab sampling. \todo{zahlen}
Therefore, we report only results for grab sampling from streams.

The analysed dataset comprised 42236 samples from 3049 sampling sites (Figure \ref{fig:fig1} and Supplement). 
We found big differences in the number of sampling sites between federal states.

The dataset include 484

@@

>>>>

Small water bodies are important refuges of biodiversity \citep{davies_comparison_2008} and enabling downstream colonisation of polluted streams \citep{liess_analyzing_2005}.
At the same time they may be exposed to a high risk of pesticide contamination from adjacent agricultural areas and low dilution effects \citep{liess_determination_1999}.
Although small streams comprise a major fraction of streams \citep{nadeau_hydrological_2007} relatively little is know about their chemical and ecological status.

The aim of this study was to compile monitoring data on a national scale and to answer the questions: \\
(i) Can the currently available monitoring data used for a representative description of the pollution situation? \\
(ii) Are small agricultural waters more polluted compared to bigger streams? Are there thresholds in these relationships? \\
(iii) baHow polluted are small streams and which pesticides are responsible?

@@

The compiled dataset comprised only few standing waters (58 sites) and the majority (90\%) of samples where taken via grab sampling.  % see clean.R for numbers
Therefore, we report only results of grab samples from streams. 
The analysed dataset comprised 42899 samples from 3049 sampling sites (Figure \ref{fig:fig1} and Supplement, Table \todo{Set ref to table}). 
We found big differences in the number of sampling sites between federal states.

484 compounds that could be classified as pesticides and their metobalites (Supplement, Table \todo{Set ref to table}) .

@@

% underestimation of grab sampling (Stehle et al. 2013).
